Virtualisierung eines Echtzeit-Betriebssystems zur Steuerung eines Roboters mit Schwerpunkt auf die Einhaltung der Echtzeit

### 2024-04-04 Masterarbeit_Robotik_Pamuk.tex
APIC_WRITE

\clearpage
\section{State of the art}

@@

@@

@@

\noindent Upon isolating a CPU to the QEMU process, it was anticipated that the guest would utilize nearly 100\% of the CPU's capacity, with minimal to no intervention from the host. However, the isolcpus function only isolates at the user level and does not affect kernel tasks. Consequently, these kernel tasks and interrupts can still utilize the CPU. This led to the investigation of the causes for the observed high and inconsistent latency. The guest operates within the kvm\_entry and \texttt{kvm\_exit} events of the host. Kernelshark revealed a high frequency of \texttt{kvm\_exit} events, indicating that the guest frequently relinquishes control of the CPU back to the host. This frequent switching hinders the guest\'s ability to run continuously, thereby increasing the virtualization latency. To further understand this, trace-cmd was employed to trace various events in the host-guest communication, including the reasons for these events. Specifically, the causes for \texttt{kvm\_exit} events were analyzed. The command sudo trace-cmd record -e all -A @3:823 --name Salamander4 -e all was executed on the host for a duration of 5 seconds. The results in Figure \ref{fig:kvm_exits} were obtained. Additionally, table \ref{tab:kvm_exit} provides a short description of the observed \texttt{kvm\_exit} events.

@@

\clearpage
Figure \ref{fig:kvm_exits_default} shows \texttt{kvm\_exit} frequency with CPU islation.
\begin{figure}[H]
	\centering
	\includegraphics[width=1.0\columnwidth]{img/kvm_exits.png}
	\caption[kvm exits]{kvm exits}
	\label{fig:kvm_exits}
\end{figure}

@@

The gnuplot latency is visible in Figure \ref{fig:gnuplot_max_max_latency_hardware}
\begin{figure}[H]
	\centering
	\includegraphics[width=0.8\columnwidth]{masterthesis-documentation/docs/sigmatek/xenomai/hardware/gnuplot_max_latency_hardware.png}
	\caption[gnuplot latency hardware]{gnuplot latency hardware}
	\label{fig:gnuplot_max_max_latency_hardware}
\end{figure}

@@

\clearpage
\chapter{Results}

@@

The Linux kernel with the Dovetail interface, which allows the kernel to handle real-time tasks with low latency.
The Cobalt real-time core, which is responsible for scheduling and executing real-time tasks.
In Xenomai 4, you need:
The Linux kernel with the EVL interface, which, like Dovetail, enables the kernel to handle real-time tasks with low latency.
The libevl library, which provides a user interface to the EVL core, allowing applications to use the real-time capabilities provided by EVL.
So, while both versions require a Linux kernel with a real-time interface (Dovetail for Xenomai 3, EVL for Xenomai 4), Xenomai 3 uses a real-time core (Cobalt), while Xenomai 4 uses a library (libevl) to provide applications with access to its real-time capabilities.

>>>>

\clearpage
\section{State of the art}
\clearpage

@@

\begin{comment}

@@

\end{comment}

@@

\noindent Upon isolating a CPU to the QEMU process, it was anticipated that the guest would utilize nearly 100\% of the CPU's capacity, with minimal to no intervention from the host. However, the isolcpus function only isolates at the user level and does not affect kernel tasks. Consequently, these kernel tasks and interrupts can still utilize the CPU. This led to the investigation of the causes for the observed high and inconsistent latency. The guest operates within the kvm\_entry and \texttt{kvm\_exit} events of the host. Kernelshark revealed a high frequency of \texttt{kvm\_exit} events, indicating that the guest frequently relinquishes control of the CPU back to the host. This frequent switching hinders the guest\'s ability to run continuously, thereby increasing the virtualization latency. To further understand this, trace-cmd was employed to trace various events in the host-guest communication, including the reasons for these events. Specifically, the causes for \texttt{kvm\_exit} events were analyzed. The command sudo trace-cmd record -e all -A @3:823 --name Salamander4 -e all was executed on the host for a duration of 5 seconds. The results in Figure \ref{fig:kvm_exit_taskset} were obtained. Additionally, table \ref{tab:kvm_exit} provides a short description of the observed \texttt{kvm\_exit} events.

@@

\clearpage
Figure \ref{fig:kvm_exits_default} shows \texttt{kvm\_exit} frequency with CPU islation.
\begin{figure}[H]
	\centering
	\includegraphics[width=1.0\columnwidth]{img/kvm_exits_taskset.png}
	\caption[kvm exits]{kvm exits}
	\label{fig:kvm_exit_taskset}
\end{figure}

@@

The gnuplot latency is visible in Figure \ref{fig:gnuplot_max_latency_hardware}
\begin{figure}[H]
	\centering
	\includegraphics[width=0.8\columnwidth]{masterthesis-documentation/docs/sigmatek/xenomai/hardware/gnuplot_max_latency_hardware.png}
	\caption[gnuplot latency hardware]{gnuplot latency hardware}
	\label{fig:gnuplot_max_latency_hardware}
\end{figure}

@@

\chapter{Latency Reduction}
\section{CPU isolation}
\clearpage
\section{User and Kerneltasks}
\clearpage
\section{IRQ}
\clearpage

\chapter{KVM exit reasons}
\section{APIC\_WRITE}

The Advanced Programmable Interrupt Controller (APIC) is responsible for the distribution of interrupts in x86 and Itanium-based computer systems. It consists of two main components: the I/O APIC and the local APICs. The I/O APIC receives interrupt requests from devices and distributes them as messages to the Local APICs. The Local APICs then forward the highest-priority interrupt to the CPU core. The APIC offers many advantages, including more inputs for interrupts, a flexible configuration, definable priorities and support for message-signalled interrupts.

\cite{lutsykPipelinedMulticoreMachine2020}
%https://www.wikiwand.com/de/Advanced_Programmable_Interrupt_Controller

\subsection{APIC virtualization}

Newer Intel processors offer hardware virtualization of the Advanced Programmable Interrupt Controller (APICv). APICv improves virtualized AMD64 and Intel 64 guest performance by allowing the guest to directly access the APIC, dramatically cutting down interrupt latencies and the number of virtual machine exits caused by the APIC. This feature is used by default in newer Intel processors and improves I/O performance.

\clearpage
\section{HLT}
\subsection{Description}
\subsection{Occurence Reduction}
\clearpage
\section{EPT\_MISCONFIG}
\subsection{Description}
\subsection{Occurence Reduction}
\clearpage
\section{PREEMPTION\_TIMER}
\subsection{Description}
\subsection{Occurence Reduction}
\clearpage
\section{EXTERNAL\_INTERRUPT}
\subsection{Description}
\subsection{Occurence Reduction}
\clearpage
\section{IO\_INSTRUCTION}
\subsection{Description}
\subsection{Occurence Reduction}
\clearpage
\section{EOI\_INDUCED}
\subsection{Description}
\subsection{Occurence Reduction}
\clearpage
\section{EPT\_VIOLATION}
\subsection{Description}
\subsection{Occurence Reduction}
\clearpage
\section{PAUSE\_INSTRUCTION}
\subsection{Description}
\subsection{Occurence Reduction}
\clearpage
\section{CPUID}
\subsection{Description}
\subsection{Occurence Reduction}
\clearpage
\section{MSR\_READ}
\subsection{Description}
\subsection{Occurence Reduction}
\clearpage

\chapter{Results}

\begin{comment}

@@

The Linux kernel with the Dovetail interface, which allows the kernel to handle real-time tasks with low latency.
The Cobalt real-time core, which is responsible for scheduling and executing real-time tasks.
In Xenomai 4, you need:
The Linux kernel with the EVL interface, which, like Dovetail, enables the kernel to handle real-time tasks with low latency.
The libevl library, which provides a user interface to the EVL core, allowing applications to use the real-time capabilities provided by EVL.
So, while both versions require a Linux kernel with a real-time interface (Dovetail for Xenomai 3, EVL for Xenomai 4), Xenomai 3 uses a real-time core (Cobalt), while Xenomai 4 uses a library (libevl) to provide applications with access to its real-time capabilities.
\end{comment}
